Tropical Andes IUCN Montane and Lowland forest

### 2023-10-04 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
add aggregation and type conversion code

# Crop moist montane to Tropical Andes
```{r}
iucn_moist_montane_forest_crop <- crop(iucn_moist_montane_forest, study_region)
TA_iucn_moist_montane_forest <- mask(iucn_moist_montane_forest_crop, study_region)
plot(TA_iucn_moist_montane_forest)
TA_iucn_moist_montane_forest
```

# Crop moist lowland to Tropical Andes
```{r}
iucn_moist_lowland_forest_crop <- crop(iucn_moist_lowland_forest, study_region)
TA_iucn_moist_lowland_forest <- mask(iucn_moist_lowland_forest_crop, study_region)
plot(TA_iucn_moist_lowland_forest)
TA_iucn_moist_lowland_forest
```

@@

# Save raster
```{r}
writeRaster(TA_iucn_habitat_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest.GTiff"), format = "GTiff", overwrite=TRUE)
writeRaster(TA_iucn_moist_montane_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest_Montane.GTiff"), format = "GTiff", overwrite=TRUE)
writeRaster(TA_iucn_moist_lowland_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest_Lowland.GTiff"), format = "GTiff", overwrite=TRUE)
```

>>>>

## Crop moist montane
```{r}
iucn_moist_montane_forest_crop <- crop(iucn_moist_montane_forest, study_region)
TA_iucn_moist_montane_forest <- mask(iucn_moist_montane_forest_crop, study_region)
plot(TA_iucn_moist_montane_forest)
TA_iucn_moist_montane_forest
```

## Crop moist lowland
```{r}
iucn_moist_lowland_forest_crop <- crop(iucn_moist_lowland_forest, study_region)
TA_iucn_moist_lowland_forest <- mask(iucn_moist_lowland_forest_crop, study_region)
plot(TA_iucn_moist_lowland_forest)
TA_iucn_moist_lowland_forest
```

@@

# Save raster
```{r}
writeRaster(TA_iucn_habitat_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest.GTiff"), format = "GTiff", overwrite=TRUE)
writeRaster(TA_iucn_moist_montane_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest_Montane.GTiff"), format = "GTiff", overwrite=TRUE)
writeRaster(TA_iucn_moist_lowland_forest, filename = file.path(output_path, "TropicalAndes_IUCNHabitat_Forest_Lowland.GTiff"), format = "GTiff", overwrite=TRUE)
```
# Aggregate to 0.3
```{r}
TropicalAndes_IUCNHabitat_Forest0.3 <- aggregate(TropicalAndes_IUCNHabitat_Forest, 30, fun=mean, na.rm=TRUE)
TropicalAndes_IUCNHabitat_Forest0.3
```

```{r}
writeRaster(TropicalAndes_IUCNHabitat_Forest0.3,file.path(output_path, "TropicalAndes_IUCNHabitat_Forest0.3.tif"), overwrite = TRUE)
```

# Forest shape conversion
```{r}
TropicalAndes_IUCNHabitat_Forest <- aggregate(TropicalAndes_IUCNHabitat_Forest, 50, fun=mean, na.rm=TRUE)
TropicalAndes_IUCNHabitat_Forest
```

```{r}
Forest_poly <- rasterToPolygons(TropicalAndes_IUCNHabitat_Forest, na.rm = TRUE, dissolve = TRUE)
Forest_poly
plot(Forest_poly)
```

```{r}
Forest_sf <- st_as_sf(Forest_poly)
Forest_sf
plot(Forest_sf)
st_write(Forest_sf, file.path(data_path, "Forest_sf.shp"))
```
